---
title: "Silly game suite<br>(DDP Assignment Week 4)"
author: "Agne Larsson"
date: "September 23, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R U Bored?

- Waiting for results from a complex computing algo? (1h)
- Taking part in an uninteresting meeting? (2h)
- Was your flight delayed for hours? (3h)

```{r, echo = TRUE}
algo <- 1; meeting <- 2; airport <- 3
(hours_to_kill <- sum(algo, meeting, airport))
```
**Need something _(mildly)_ entertaining to do in the meantime?**

What you need is...

(well, go to the next slide already!)

## Agnepagne's silly game suite

```{r, echo = FALSE}
par(mfrow=c(1,2))
x <- runif(50, 0, 100)
y <- x - rnorm(50, 0, 50)
plot(x, y, axes = F, main = "Correctelate")
m <- matrix(as.numeric(rbinom(20*20, 1, .3)), 20, 20)
image(m, col = c("white", "black"), axes = F, main = "Sharea")
```
<center>http://agnepagne.shinyapps.io/ddp_assignment_week4</center>

## Correctelate

In this game, you see a plot and have to guess the correlation between x and y. Entertaining and educating. Sort of.

```{r, echo = FALSE}
par(mfrow=c(1,2))
x <- runif(50, 0, 100)
y <- - x + rnorm(50, 0, 50)
plot(x, y, axes = F)
x <- runif(50, 0, 100)
y <- x + rnorm(50, 0, 10)
plot(x, y, axes = F)
```

## Sharea

In this game, you have to guess what proportion of the area is black. Surprisingly fun. Surprisingly useless.

```{r, echo = FALSE}
par(mfrow=c(1,2))
m1 <- matrix(as.numeric(rbinom(20*50, 1, .1)), 20, 50)
m2 <- matrix(as.numeric(rbinom(100*15, 1, .8)), 100, 15)
image(m1, col = c("white", "black"), axes = F)
image(m2, col = c("white", "black"), axes = F)
```
